Fourmile

### 2022-09-01 fourmile_dataprocess.Rmd
filtering tipping buckets for non rain months

```{r precip, echo=F}
#daily precip
daily_p <- prec %>%
  replace(.==-9999, NA) %>%
  mutate(date = dmy(date)) %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date)) %>%
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))

>>>>

```{r precip, echo=F}
#daily precip
prec_update <- prec %>%
    replace(.==-9999, NA) %>%
  mutate(date = dmy(date),
         doy = yday(date)) %>%
  mutate(Gordon_South = ifelse(!doy %in% c(152:258), 
                               NA, Gordon_South),
         Gordon_North = ifelse(!doy %in% c(152:258), 
                               NA, Gordon_North),
         GH = ifelse(!doy %in% c(152:258), 
                               NA, GH),
         LM = ifelse(!doy %in% c(152:258), 
                               NA, LM),
         SE = ifelse(!doy %in% c(152:258), 
                               NA, SE),
         SP = ifelse(!doy %in% c(152:258), 
                               NA, SP),
         ST = ifelse(!doy %in% c(152:258), 
                               NA, ST),
         NADP_SL = ifelse(!doy %in% c(152:258), 
                               NA, NADP_SL))

daily_p <- prec %>%
  pivot_longer(!date, names_to = 'site', values_to = 'precip_mm') %>%
  mutate(precip_mm = as.numeric(precip_mm)) %>%
  mutate(WY = calcWaterYear(date))
  group_by(WY, site) %>%
  mutate(dailyp_cum_mm = cumsum(precip_mm))
